The case for open preprints in biology

### 2013-03-28 ms.tex
add ref

Despite the success of this approach in other fields, most manuscripts in
biology are not posted to preprint servers and are therefore not seen by more
than a handful of other scientists prior to publication. In this article, we
highlight the advantages of open preprint servers for both scientists and
publishers, discuss the preprint policies of major publishers in biology, and
describe the main options to publish preprints (Box 1, Table 2).

@@

There are a number of reasons why biologists have not developed a culture of
sharing preprints, many of which are based on common misconceptions. For
example, in contrast to other fields there is a perception in biology that
public preprints make it easier to steal ideas \cite{gin11}. In other fields
preprints serve the opposite role, they allow straightforward establishment
of precedence, letting research lay claim to an idea thus preventing it from
being ``stolen'' \cite{gin11}. Another major concern is based on a certain
interpretation of the Ingelfinger rule: scientists should not publish the
same manuscript twice \cite{alt96}. A preprint is simply a document that
allows ideas to spread and be discussed, it is not yet formally validated by
the peer-review system. This is why almost all the major publishers in
biology are preprint-friendly, including: Nature Publishing Group, PLOS,
BMC, PNAS, Elsevier, and Springer (Table 1). This year, both the Ecological
Society of America and the Genetics Society of America changed their
policies to allow public preprints. \emph{Nature} even felt compelled to
respond to the rumour that they refused manuscripts submitted to arXiv by
saying that ``\emph{Nature} never wishes to stand in the way of
communication between researchers. We seek rather to add value for authors
and the community at large in our peer review, selection and editing'' \cite
{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
towards preprints, mostly due to the lack of clear policy of the publishers.
As an example, Wiley-Blackwell, which publishes some of the leading journals
in biology, has no official policy on the matter.

@@

\subsection*{Figure 1 (map.tiff)}

@@

\subsection*{Figure 2 (arxiv.tiff)}

@@

Some publishers tolerate preprints except for a few of their medical
journals, for example the \emph{ Journal of the National Cancer Institute}
from Oxford and \emph{The Lancet} from Elsevier.

@@

>>>>

Despite the success of this approach in other fields, most manuscripts in
biology are not posted to preprint servers and are therefore not seen by more
than a handful of other scientists prior to publication. In this article, we
highlight the advantages of open preprint servers for both scientists and
publishers, discuss the preprint policies of major publishers in biology, and
describe the main options to publish preprints (Box 1, Table 1).

@@

There are a number of reasons why biologists have not developed a culture of
sharing preprints, many of which are based on common misconceptions. For
example, in contrast to other fields there is a perception in biology that
public preprints make it easier to steal ideas \cite{gin11}. In other fields
preprints serve the opposite role, they allow straightforward establishment
of precedence, letting research lay claim to an idea thus preventing it from
being ``stolen'' \cite{gin11}. Another major concern is based on a certain
interpretation of the Ingelfinger rule: scientists should not publish the
same manuscript twice \cite{alt96}. A preprint is simply a document that
allows ideas to spread and be discussed, it is not yet formally validated by
the peer-review system. This is why almost all the major publishers in
biology are preprint-friendly, including: Nature Publishing Group, PLOS,
BMC, PNAS, Elsevier, and Springer (Table 2). This year, both the Ecological
Society of America and the Genetics Society of America changed their
policies to allow public preprints. \emph{Nature} even felt compelled to
respond to the rumour that they refused manuscripts submitted to arXiv by
saying that ``\emph{Nature} never wishes to stand in the way of
communication between researchers. We seek rather to add value for authors
and the community at large in our peer review, selection and editing'' \cite
{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
towards preprints, mostly due to the lack of clear policy of the publishers.
As an example, Wiley-Blackwell, which publishes some of the leading journals
in biology, has no official policy on the matter.

@@

\subsection*{Figure 1 (map.tif)}

@@

\subsection*{Figure 2 (arxiv.tif)}

@@

@@

Some publishers tolerate preprints except for a few of their medical
journals, for example the \emph{ Journal of the National Cancer Institute}
from Oxford and \emph{The Lancet} from Elsevier. Data from \cite{war12}.
